Equalizer\\Programming and User Guide

### 2013-03-20 Developer/ProgrammingGuide/paper.tex
Update for Eyescale/Equalizer#204

\textcopyright 2007-2012 \htmladdnormallink{Eyescale Software GmbH}
{http://www.eyescale.ch}. All rights reserved. No permission is
granted to copy, distribute, or create derivative works from the
contents of this electronic documentation in any manner, in whole or in
part, without the prior written permission of Eyescale Software GmbH.

@@

\clearpage
\pagenumbering{roman}
\pagestyle{headings}
\tableofcontents
%\clearpage
\listoffigures \vfill
\section*{Revision History}
{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Revision for Equalizer 0.5\\
    1.4     & Nov 25, 2008 & Revision for Equalizer 0.6\\
    1.6     & Aug 07, 2009 & Revision for Equalizer 0.9\\
    1.8     & Mar 21, 2011 & Revision for Equalizer 1.0\\
    1.10    & Feb 17, 2012 & Revision for Equalizer 1.2\\
    1.12    & Jul 20, 2012 & Revision for Equalizer 1.4\\
    \hline
  \end{tabularx}}
\clearpage

@@

The configuration tries to set up a tracking device for head tracking. Equalizer
does not provide extensive support for tracking devices, as this is an
orthogonal problem to parallel rendering. Tracking device support has already
been solved by a number of implementations, such as VRCO Trackd, VRPN and
others, which have proven to be easily integrated with Equalizer. The example
code in \textsf{eqPly} provides a reference implementation for the integration
of such a tracking library. \sref{sTracking} provides more background on head
tracking.

{\footnotesize\lstinputlisting[firstline=96, lastline=113]
  {../../../Equalizer/examples/eqPly/config.cpp}}

@@

{\footnotesize\lstinputlisting[firstline=125, lastline=133]
  {../../../Equalizer/examples/eqPly/config.cpp}}

@@

>>>>

\textcopyright 2007-2013 \htmladdnormallink{Eyescale Software GmbH}
{http://www.eyescale.ch}. All rights reserved. No permission is
granted to copy, distribute, or create derivative works from the
contents of this electronic documentation in any manner, in whole or in
part, without the prior written permission of Eyescale Software GmbH.

@@

\clearpage
\pagenumbering{roman}
\pagestyle{headings}
\tableofcontents
%\clearpage
\listoffigures \vfill
\section*{Revision History}
{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Revision for Equalizer 0.5\\
    1.4     & Nov 25, 2008 & Revision for Equalizer 0.6\\
    1.6     & Aug 07, 2009 & Revision for Equalizer 0.9\\
    1.8     & Mar 21, 2011 & Revision for Equalizer 1.0\\
    1.10    & Feb 17, 2012 & Revision for Equalizer 1.2\\
    1.12    & Jul 20, 2012 & Revision for Equalizer 1.4\\
    1.11.1  & Mar 20, 2013 & Adapt to new head tracking event\\
    \hline
  \end{tabularx}}
\clearpage

@@

@@

{\footnotesize\lstinputlisting[firstline=106, lastline=114]
  {../../../Equalizer/examples/eqPly/config.cpp}}

@@

Tracking events are often delivered asynchronously by an external source. The
recommended way to integrate them into Equalizer is to emit an
\textsf{OBSERVER\_MOTION} event, which has to contain the observer's object
identifier and a \textsf{Matrix4f} head matrix. Equalizer optionally implements
camera-based head tracking using OpenCV, and uses this mechanism to inject the
asynchronously computed tracking matrix:

{\footnotesize\lstinputlisting[firstline=194, lastline=195]
  {../../../Equalizer/eq/client/cvTracker.cpp}}

This event will be dispatched to the given observer instance in the application
process during the next \textsf{Config::handleEvents}. The observer will update
its head matrix based on the event data:

{\footnotesize\lstinputlisting[firstline=92, lastline=97]
  {../../../Equalizer/eq/client/observer.cpp}}
